\documentclass{article}

\usepackage[ampersand]{easylist}
\usepackage{float}
\usepackage{amsmath}

\usepackage{geometry}
\usepackage{pdflscape}

\begin{document}

\begin{easylist}[itemize]
& MVEA Discussant
&& Results for employment
&&& Might have used total employment, rather than change in employment.
& SEA Discussant
&& Agrawal, "Local Fiscal Competition: An Application to Sales Taxation with Multiple Federations," JUE (forthcoming)
&& Estimates for MSA's
&& Estimates for Urban/Rural areas
&& Estimates for each Region
&& Estimates for Recipricol Agreements
&& some clarifications (taxes, assignment procedure
& Georgeanne Edits
&& COMPLETED: Lit Review, Theory, Data, Conclusions
&& TODO: empirical design, results, introduction
\end{easylist}

\newpage
\begin{landscape}
\input{../analysis/output/_--_rd_results.tex}
\end{landscape}

\newpage

\section{MVEA}

\input{../analysis/output/_--_emp_rd_results.tex}

\newpage
\section{SEA}

\input{../analysis/output/_--_region_rd_results.tex}
\newpage
\input{../analysis/output/_--_metro_rd_results.tex}
\newpage
\input{../analysis/output/_--_agreements_rd_results.tex}

\section{Georgeanne Edits}

\section{Resampling Procedure}

First, let $i = 1,...,N$ be all of our matched county pairs, and $t = 1,...,T$ be each time period. We can then write our model as,

$y_{it} = X_{it}\beta + e_{it}$
Where $y_{it}$ is the difference in logged firm start up rates, and $X_{it}$ is our differenced independent variables.

Then, our model becomes the usual POLS estimator.

$$\hat \beta = (\frac{1}{TN}\sum_{t=1}^{T}\sum_{i=1}^{N}x_{it}'x_{it})^{-1}(\frac{1}{TN}\sum_{t=1}^{T}\sum_{i=1}^{N}x_{it}'y_{it})$$

Let us assume for simplicitly we only have state level independent variables (which is true for most of our estimated models). Then, let $g = 1,...,G$ be the number of \textit{state-pairs} in our sample, and $k = 1,...,N_{g}$ be the state-pair specific number of matched county pairs. Letting $\bar G = \sum_{g=1}^{G}N_{g}/G$ be the average number of state-pair matched county pairs, note that $N = \sum_{g=1}^{G}N_{g}$. Therefore, $N = \frac{\sum_{g=1}^{G}N_{g}}{G}G = \bar G G$

we can rewrite our modeol to be, $y_{kgt} = X_{gt}\beta+e_{igt}$, and our estimator to be
$$\hat \beta = (\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}\frac{N_{g}}{\bar G}x_{gt}'x_{gt})^{-1}(\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{gt}'\frac{(\sum_{k=1}^{N_{g}}y_{kgt})}{\bar G})$$

Now, we can plug back in our original model,
\begin{align*}\hat \beta &= (\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}\frac{N_{g}}{\bar G}x_{gt}'x_{gt})^{-1}(\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{gt}'\frac{(\sum_{k=1}^{N_{g}}x_{gt}\beta+e_{kgt})}{\bar G}) \\
 &=  (\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}\frac{N_{g}}{\bar G}x_{gt}'x_{gt})^{-1}(\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}\frac{N_{g}}{\bar G}x_{gt}'x_{gt}\beta +x'_{gt}\frac{(\sum_{k=1}^{N_{g}}e_{kgt})}{\bar G}) \\
 &= \beta + (\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}\frac{N_{g}}{\bar G}x_{gt}'x_{gt})^{-1}(\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x'_{gt}\frac{(\sum_{k=1}^{N_{g}}e_{kgt})}{\bar G}) \end{align*}

The result of this is that we see that our estimator appears to be a weighted estimate of the data in our sample. In particular, counties that have more than $\bar G$ worth of observations get underweighted compared to their mean, and counties that have less than $\bar G$ worth of matched county pairs get overweighted compared to their mean.

An example of this would be, imagine we only had 4 states in our sample, Texas-Oklahoma, and Maryland-Delaware. TX-OK has 35 matched county pairs per year, and MD-DL has 2. As a result, the mean is 17.5. Then, when we go to compute our estimate, the estimator over emphasizes interactions along TX-OK's border, and underweights interactions along MD-DL's border. (We can see this when I went to do the Rural v Urban estimates, and how property tax appeared. Many of the states with higher observation counts appear in more rural counties.

As a result, I (starting last spring) was also calculating a Donald and Lang (2007) two-stage estimator. The first stage is to simply take averages along each border, and then take the difference. This leads to the alternative estimator,

Now note that $E(y_{tg})$ is the average for each side of the border. By construction, this is equal to,

$$E(y_{tg}) = x_{tg}\beta+E(e_{tg})$$

Thus this model requires the same assumptions we make for our first model. We can then compute the estimator as follows.

\begin{align*}\hat \beta' &= (\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{tg}'x_{tg})^{-1}(\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{tg}'E(y_{tg})) \\ 
&= (\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{tg}'x_{tg})^{-1}(\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{tg}' x_{tg}\beta+x_{tg}'E(e_{tg})) \\
&= \beta + (\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{tg}'x_{tg})^{-1}(\frac{1}{TG}\sum_{t=1}^{T}\sum_{g=1}^{G}x_{tg}'E(e_{tg})) \end{align*}

\end{document}